```{r setup, include = F, warning = F, message = F}
options(java.parameters = "-Xmx16G")
library(tidyverse)
library(lubridate)
library(haven)
library(RJDBC)
library(knitr)
library(rmarkdown)
setwd("N:/ORP_accountability")

# Load accountability results
s = read_csv("projects/2018_school_accountability/school_grading_grades.csv")
m = read_csv("projects/2018_school_accountability/school_grading_metrics.csv")
d = read_csv("data/2018_final_accountability_files/2018_district_accountability_file_JW.csv")

```

---
title: "Accountability Model Evaluation"
author: "Assessment, Accountability, and Data Governance"
date: `r str_c(month(today(), label = T, abbr = T), ". ", day(today()), ", ", year(today()))`
output: html_document
---
***
#### Document Overview
This document evaluates the `r ifelse(between(month(today()), 1, 4), year(today()) - 1, year(today()))` accountability methodology and results. 

The model followed four guiding principles:
* All schools should have the opportunity to earn a high score.
    + Poverty is not destiny.
* All means all.
    + Each indicator should be reported for historically underserved student groups.
* All growth should be rewarded.
    + Schools with low achievement but high growth will be recognized.
    + Incremental growth will be recognized.
* Reporting should be transparent.
    + The public should be able to access and review multiple indicators.


```{r, echo = F, warning = F, message = F}
# 


```

***
 
#### __Model 1__: Bottom 5% of Overall Average, Multiple Years of Data

```{r, echo = F, include = F}
# file.copy(from = str_c("N:/ORP_accountability/projects/Evan/Accountability/Analysis/Output/Evaluation/", 
#                        year(today()) + 1, "_school_modeling.html"),
#           to = str_c("N:/ORP_accountability/projects/", 
#                      year(today()) + 1, 
#                      "_school_modeling/Output/", 
#                      str_replace_all(today(), "-", ""),
#                      "_school_modeling_notes.html"),
#           overwrite = T)
```